How to Name a Real-World Object, and how not to

### 2019-12-07 papers/ACL2020/manynames.tex
clarify stability remark

\paragraph{Identifying entry-level names requires many annotators}
ManyNames was collected in four rounds of 9 annotators each.
On average, the most frequent names differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
\begin{figure}[t]
	\includegraphics[width=\columnwidth]{images/stability_analytic.png}
	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the most frequent name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
The blue line shows that, even after gathering 10 names, the entry-level name has been confidently identified for only 68\% of objects.
Gathering 20 names increases this to 78\%.
The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names does not allow us to confidently state which name is the entry-level name: differences in frequencies between the contenders are simply too small.
\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper. I lack a proper overview to be able to tell.}

>>>>

\paragraph{Identifying entry-level names requires many annotators}
ManyNames was collected in four rounds of 9 annotators each.
On average, the most frequent names differed between rounds for 20\% of objects (std.dev. 2.4\%p), suggesting that entry-level names cannot be reliably identified from too few annotators.
Figure~\ref{fig:entry-level-name-stability} shows this in a more general way.
\mw{@gbt: I first did it the way you suggested, i.e., by sampling, but I found the resulting plot (not shown now) too hard to interpret, even a bit misleading. I've kept this text + plot in the TeX source further below, commented out, in case you want to have a look. But I think the following is better:}
\begin{figure}[t]
	\includegraphics[width=\columnwidth]{images/stability_analytic.png}
	\caption{Proportion of objects (vertical) for which the entry-level name can be confidently (95\%) identified after gathering N names (horizontal). \mw{increase plot font size}}
	\label{fig:entry-level-name-stability}
\end{figure}
For each object we computed, on the basis of the distribution of names in ManyNames for that object, how many names should have been gathered for the majority name among them to be the entry-level name (as defined on the basis of 36 names) with 95\% probability (a reasonable confidence requirement).
The blue line shows that, even after gathering 10 names, the entry-level name has been confidently identified for only 68\% of objects.
Gathering 20 names increases this to 78\%.
The red line shows the same tendency but by taking only names from the entry-level cluster into account (as identified by our Verification results):
by discarding names for other objects, the entry-level name for the intended object can be confidently identified slightly more quickly (but not by much, since names for the wrong object tend to be a minority anyway).
Both lines level level out well below 100\%, reflecting that for 15\%-20\% of objects even gathering 36 names is not enough for the majority name to be confidently assumed to be the entry-level name: differences in frequencies between the contenders are simply too small.
\mw{@cs, @sz: I wonder how this is / ought to be taken into account in other analyses in the paper. I think the difference between sample majority name and population majority name could be useful? I lack a proper overview to be able to tell.}
